Mirror Match: Reliable Feature Point Matching Without Geometric Constraints

### 2013-08-01 text/clustering.tex
report is now submitted version

position in the image,
and the method from \cite{wu2011robust}, which uses maximally stable 
extremal regions (MSER) feature points to designate areas. %In this 
paper the algorithm from \cite{das2008event} will later be referred to 
as \emph{Isodata}.

@@

In practice there are many situations where relying on the geometry of the 
image to filter correspondences is not possible, for example images without overlap, or adjacent objects in one image are that are separated in 
another.  %Another example is images that do not overlap where algorithms might still find matches adhering to the imposed geometric constraints.
Furthermore, methods using geometric constraints all require an initial 
set of correspondences. If this set of correspondences can be narrowed down 
to the most probable correct matches, the geometric matching algorithm will benefit in terms of speed and accuracy. 
Finally some use cases might require a speed that simply cannot be achieved by 
complex geometric methods.% where simple non geometric methods might be able to provide sufficient matching accuracy with a smaller performance penalty.

In the absence of geometric constraints, only few methods are available. 
As pointed out in \cite{szeliski2010}, the simplest 
approach to matching feature points is to return all matches above a given 
threshold of similarity.  This can be done with a fixed threshold or by 
finding the nearest neighbors for each point (still filtering by a threshold to avoid including matches for feature points that have no counterpart in the other image).  
Lowe \cite{lowe2004sift} proposed the scale-invariant feature transform (SIFT) together with 
an alternative measure, where the uniqueness of a given match is found by 
looking at the two nearest neighbors of each feature point and 
calculating the matching score as the ratio of similarities.  Ranking the 
scores by their uniqueness and picking the $n$ best produces a set of 
correspondences that are distinctly matched across two images. %This method will be referred to as \emph{SIFT} in this paper. 
Of these three methods (fixed threshold, nearest neighbors, and \emph{SIFT}), 
\emph{SIFT} was found to perform best by a slight margin 
\cite{mikolajczyk2005performance}.

>>>>

position in the image, and the method from \cite{wu2011robust}, which 
uses maximally stable extremal regions (MSER) feature points to 
designate areas. In this paper the algorithm from \cite{das2008event} 
will later be referred to as \emph{Isodata}.

@@

In practice there are many situations where relying on the geometry of 
the image to filter correspondences is not possible, for example images 
without overlap, or adjacent objects in one image are that are separated 
in another.  Furthermore, methods using geometric constraints all 
require an initial set of correspondences. If this set of 
correspondences can be narrowed down to the most probable correct 
matches, the geometric matching algorithm will benefit in terms of speed 
and accuracy.  Finally some use cases might require a speed that simply 
cannot be achieved by complex geometric methods.

In the absence of geometric constraints, only few methods are available.  
As pointed out in \cite{szeliski2010}, the simplest approach to matching 
feature points is to return all matches above a given threshold of 
similarity.  This can be done with a fixed threshold or by finding the 
nearest neighbors for each point (still filtering by a threshold to 
avoid including matches for feature points that have no counterpart in 
the other image).  Lowe \cite{lowe2004sift} proposed the scale-invariant 
feature transform (SIFT) together with an alternative measure, where the 
uniqueness of a given match is found by looking at the two nearest 
neighbors of each feature point and calculating the matching score as 
the ratio of similarities.  Ranking the scores by their uniqueness and 
picking the $n$ best produces a set of correspondences that are 
distinctly matched across two images.
Of these three methods (fixed threshold, nearest neighbors, and 
\emph{SIFT}), \emph{SIFT} was found to perform best by a slight margin 
\cite{mikolajczyk2005performance}.
